Bricking up and overgrowing backdoors in Intrusion Detection Systems

### 2019-09-06 ex2/paper/paper.tex

\subsubsection{Spotting Backdoors}
Backdoors can be identified by computing PDP and or ALE plots for the \gls{mui} and investigating if regions exist which have counter-intuitive model predictions.
\subsection{Pruning Techniques}
\subsubsection{Neural Network Pruning}
\subsubsection{Random Forest Pruning}
For intrusion detection decision tree based models or random forests of decision trees have been shown to usually achieve higher accuracy than multilayer perceptrons \todo{citation needed} and moreover they are generally faster to train and possibly more interpretable. For \glspl{nids} we thus consider the removal of backdoors from decision tree based models to be a more pressing issue than from multilayer perceptrons.

>>>>

\subsubsection{Identifying Backdoors}
Backdoors can be identified by computing \gls{pdp} and or \gls{ale} plots for the \gls{mui} and investigating if regions exist which the \gls{mui} behaves counter-intuitive. For our \gls{rf} model, \autoref{fig:pdp_ttl} shows the \gls{pdp} for the \gls{ttl} value in forward direction. 
\subsection{Pruning Techniques}
\subsubsection{Neural Network Pruning}
\subsubsection{Random Forest Pruning}
For intrusion detection decision tree based models or random forests of decision trees have been shown to usually achieve higher accuracy than multilayer perceptrons \todo{citation needed} and moreover they are generally faster to train and possibly more interpretable. For \glspl{nids} we thus consider the removal of backdoors from decision tree based models to be a more pressing issue than from multilayer perceptrons.
